---
title: "Analysis"
author: "Jumoke Ajakaiye and Ricardo David Barragan Martinez"
date: "5/23/2021"
output: html_document
---

# Animals slaughtered for meat

## A glance at the data

```{r include=FALSE}
library(readr)
library(dplyr)
library(ggplot2)
library(tidyr)
library(janitor)
```

```{r load the global meat production data set, include=FALSE}
global_meat_production <- data.frame( read_csv("archive (5)/global-meat-production.csv"))
```

```{r}
#Getting the head of the DS.
head(global_meat_production)
```


```{r summary of data animals slaughtered DS, echo=FALSE}
#Summary of data set
summary(global_meat_production)
```

## Observing the data with graphs before cleaning

```{r plot by year and production from 1961 to 2018,echo=FALSE}
#added the title, subtitle, ylab, and caption)

ggplot(global_meat_production, aes(x = Year, y =global_meat_production$`Livestock.Primary...Meat..Total...1765...Production...5510...tonnes..tonnes.`)) +  
  labs(title = "World Meat Production Datasets 1961 - 2018", subtitle = "Global Meat Production", caption = "Data from Food and Agriculture Organization")+
  ylab("Livestock Primary")+
  geom_line(aes(color = Year), size = 1) + theme_minimal()
```

### Analysing the NA values

```{r observing NA values, echo=FALSE}
#Observing data with NA values

global_meat_production[rowSums(is.na(global_meat_production)) > 0,]
```

Observing the NA values with NA values in the code column

```{r observing data with NA values in the values column,echo=FALSE}
#Observing data with NA values in the code column
#The data with NA in Code are continents or regions. The information should not be considered.

global_meat_production[is.na(global_meat_production$country_code), ]
```

Cleaning the columns and renaming 

```{r}
#Formatted the columns titles to lowercase

global_meat_production <- clean_names(global_meat_production)
```


```{r}
#Used the pipe operator to rename the columns

global_meat_production <- global_meat_production %>% 
  rename(country = entity,
         country_code = code, 
         livestock_primary = `livestock_primary_meat_total_1765_production_5510_tonnes_tonnes`)
```


## Data of animals slaughtered after cleaning

Head of animals slaughtered after cleaning

```{r head of animals slaughtered after cleaning, echo=FALSE}
#head of data set
head(global_meat_production)
```

Summary of animals slaughtered after cleaning

```{r summary of animals slaughtered after cleaning,echo=FALSE}
#Summary of data set
summary(global_meat_production)
```

```{r}
#Top countries with more production
head(arrange(global_meat_production,desc(global_meat_production$livestock_primary)),n = 20)
```



# New dataframe

```{r new data frame without world features}

# Filtered OWID_WRL
# Created new dataframe to run the following codes below.
# We can also edit it back to the original dataframe
# Once we figure out why the code on line 99 didn't work for me

global_mp <- filter(global_meat_production, country_code != "OWID_WRL")
```



```{r list of countries}
#Save a new DF to observe the country and country codes. This will be useful to observe the countries that could mislead the analysis. 
list_countries <- unique(global_mp[c("country", "country_code")])
```




```{r head of countries without the regional (e.g. Europe) numbers}
#Observe top countries and produciton
head(arrange(global_mp,desc(global_mp$livestock_primary,n = 50)))
```

Observing the data with graphs after cleaning

```{r plot wiht by year and turkey after cleaning,echo=FALSE}
#global_mp dataframe
#added ylab,xlab, title, subtitle, and caption) 

ggplot(global_mp, aes(x = year, y = `livestock_primary`)) + 
  ylab("Livestock Primary")+ xlab("Year")+
  labs(title = "World Meat Production Datasets 1961 - 2018", subtitle = "Global Meat Production", caption = "Data from Food and Agriculture Organization")+ 
  geom_line(aes(color = year), size = 1) +
  theme_minimal()
```


```{r plot wiht by year and turkey after cleaning,echo=FALSE}
#global_mp dataframe
#added xlab, title, subtitle, and caption) 

ggplot(global_mp) +
  aes(x = `livestock_primary`) +
  labs(title = "World Meat Production Datasets 1961 - 2018", subtitle = "Global Meat Production", caption = "Data from Food and Agriculture Organization")+
  xlab("Livestock Primary")+
  geom_histogram(bins = 30L, fill = "#0c4c8a") +
  theme_minimal()
```

```{r}
#global_mp
#edit Category to category

summ_prod_by_country <- aggregate(global_mp$livestock_primary, by = list(category = global_mp$country_code), FUN=sum)

summ_prod_by_country[order(-summ_prod_by_country$x),]
 
```

```{r finding outliers in the data}
#added title, xlab, subtitle, and caption

ggplot(summ_prod_by_country) +
  aes(x = "", y = x ) +
  xlab("Total Production per Country") +
  labs(title = "World Meat Production Datasets 1961 - 2018", subtitle = "Meat Production Total per Country", caption = "Data from Food and Agriculture Organization")+ geom_boxplot(fill = "#0c4c8a") +
  theme_minimal()
```
```{r}

top <- summ_prod_by_country %>%
    arrange(desc(x)) %>%
    slice(1:10)
```

```{r}
#edit Category to category

ggplot(data=top, aes(x=category, y=x,fill=category)) +
    geom_bar(stat="identity") +
    geom_text(aes(label=round(x/1000000)), vjust=1.6, color="black", size=3.5) + 
    theme_minimal() + 
    theme(axis.text.y = element_blank()) +
    ggtitle("Top 10 countries with more production from 1961 to 2018") +
    xlab("Countries") +
    ylab("Production in Mio.") + 
    guides(fill=FALSE)
```

```{r}
per_capita_consumption_per_year <- read_csv("archive (5)/per-capita-meat-consumption-by-type-kilograms-per-year.csv")
```

```{r load the consumption data set, include=FALSE}
head(per_capita_consumption_per_year)
```

```{r summary of data consumption, echo=FALSE}
#Summary of data set
summary(per_capita_consumption_per_year)
```

## Observing the data with graphs before cleaning

```{r plot by year and consumption from 1961 to 2018,echo=FALSE}
#added the title, subtitle, ylab, and caption)

ggplot(per_capita_consumption_per_year, aes(x = Year, y =per_capita_consumption_per_year$`Beef and bufallo (kilograms per year)`)) +  
  labs(title = "World Meat Production Datasets 1961 - 2018", subtitle = "Global Meat Production", caption = "Data from Food and Agriculture Organization")+
  ylab("Livestock Primary")+
  geom_line(aes(color = Year), size = 1) + theme_minimal()
```
### Analysing the NA values

```{r observing NA values consum, echo=FALSE}
#Observing data with NA values

per_capita_consumption_per_year[rowSums(is.na(per_capita_consumption_per_year)) > 0,]
```
Observing the NA values with NA values in the code column

```{r observing data with NA values in the values column consum,echo=FALSE}
#Observing data with NA values in the code column
#The data with NA in Code are continents or regions. The information should not be considered.

per_capita_consumption_per_year[is.na(per_capita_consumption_per_year$Code), ]
```
```{r}
#Formatted the columns titles to lowercase

per_capita_consumption_per_year <- clean_names(per_capita_consumption_per_year)
```

## Data of consumption after cleaning

Head of consumption after cleaning

```{r head of consum after cleaning, echo=FALSE}
#head of data set
head(per_capita_consumption_per_year)
```


```{r summary of consumption after cleaning,echo=FALSE}
#Summary of data set
summary(per_capita_consumption_per_year)
```

```{r}
#Top countries with more production
head(arrange(per_capita_consumption_per_year,desc(per_capita_consumption_per_year$mutton_and_goat_kilograms_per_year)),n = 20)
```

Eliminating the information with the NA values in the code column

```{r DF without NA values in code column,echo=FALSE}
#deliting the information without a code (continents information).

per_capita_consumption_per_year <- per_capita_consumption_per_year[!is.na(per_capita_consumption_per_year$code), ]
```

```{r list of countries consum}
#Save a new DF to observe the country and country codes. This will be useful to observe the countries that could mislead the analysis. 
list_countries_consum <- unique(per_capita_consumption_per_year[c("entity", "code")])
```


```{r head of countries without the regional (e.g. Europe) numbers consum}
#Observe top countries and consumption
head(arrange(per_capita_consumption_per_year,desc(per_capita_consumption_per_year$beef_and_bufallo_kilograms_per_year,n = 50)))
```


Observing the data with graphs after cleaning

```{r plot wiht by year and beef/bufalo,echo=FALSE}

ggplot(per_capita_consumption_per_year, aes(x = year, y = per_capita_consumption_per_year$beef_and_bufallo_kilograms_per_year)) + 
  ylab("Beef and bufallo kilograms per year")+ xlab("Year")+
  labs(title = "World Meat Consumption of Beef and Bufalo in kilograms from 1961 - 2018", subtitle = "Global Meat consumption", caption = "Data from Food and Agriculture Organization")+ 
  geom_line(aes(color = year), size = 1) +
  theme_minimal()
```
```{r}
row_sub = apply(per_capita_consumption_per_year, 1, function(row) all(row !="Maldives" ))
per_capita_consumption_per_year <- per_capita_consumption_per_year[row_sub,]
```

```{r}
per_capita_consumption_per_year <- per_capita_consumption_per_year[!is.na(per_capita_consumption_per_year$code), ]
```


```{r plot wiht by year and beef/bufalo without NAs,echo=FALSE}

ggplot(per_capita_consumption_per_year, aes(x = year, y = per_capita_consumption_per_year$beef_and_bufallo_kilograms_per_year)) + 
  ylab("Beef and bufallo kilograms per year")+ xlab("Year")+
  labs(title = "World Meat Consumption of Beef and Bufalo in kilograms from 1961 - 2018", subtitle = "Global Meat consumption", caption = "Data from Food and Agriculture Organization")+ 
  geom_line(aes(color = year), size = 1) +
  theme_minimal()
```

```{r}
barplot(tapply(per_capita_consumption_per_year$mutton_and_goat_kilograms_per_year, format(per_capita_consumption_per_year$year), FUN=sum))
```
```{r}
library(dplyr)
library(ggplot2)
graph_consumption_2 <- per_capita_consumption_per_year %>% 
  group_by(year) %>% 
  summarise(Data = sum(mutton_and_goat_kilograms_per_year))

ggplot(graph_consumption_2, aes(x = year, y = Data)) + 
  ylab("Mutton and goat kilograms per year")+ xlab("Year")+
  labs(title = "World Meat Consumption of mutton and goat in kilograms from 1961 - 2018", subtitle = "Global Meat consumption", caption = "Data from Food and Agriculture Organization")+ 
  geom_line(aes(color = year), size = 1) +
  theme_minimal()
```

