---
title: "Analysis"
author: "Jumoke Ajakaiye and Ricardo David Barragan Martinez"
date: "5/23/2021"
output: html_document
---

# Animals slaughtered for meat

## A glance to the data

```{r include=FALSE}
library(readr)
library(dplyr)
library(ggplot2)
library(tidyr)
```

```{r load the slaughtered data set, include=FALSE}
animals_slaughtered_for_meat <- read_csv("archive (5)/animals-slaughtered-for-meat.csv")

```

```{r changing names, include=FALSE}
#Change the name of some columns to create subsets
colnames(animals_slaughtered_for_meat)[colnames(animals_slaughtered_for_meat) == "Turkey (turkeys slaughtered)"] <- "Turkey"
colnames(animals_slaughtered_for_meat)[colnames(animals_slaughtered_for_meat) == "Pigs (pigs slaughtered)"] <- "Pigs"
colnames(animals_slaughtered_for_meat)[colnames(animals_slaughtered_for_meat) == "Cattle (cattle slaughtered)"] <- "Cattle"
colnames(animals_slaughtered_for_meat)[colnames(animals_slaughtered_for_meat) == "Goats (goats slaughtered)"] <- "Goats"
colnames(animals_slaughtered_for_meat)[colnames(animals_slaughtered_for_meat) == "Chicken (chicken slaughtered)"] <- "Chicken"
colnames(animals_slaughtered_for_meat)[colnames(animals_slaughtered_for_meat) == "Sheep (sheeps slaughtered)"] <- "Sheep"
```

Head of data animals slaughtered

```{r head of data animals slaughtered DS, echo=FALSE}
#head of data set
head(animals_slaughtered_for_meat)
```

Summary of data animals slaughtered 

```{r summary of data animals slaughtered DS, echo=FALSE}
#Summary of data set
summary(animals_slaughtered_for_meat)
```


## Observing the data with graphs before cleaning

```{r plot wiht by year and turkey,echo=FALSE}
ggplot(animals_slaughtered_for_meat, aes(x = Year, y = Turkey)) + 
  geom_line(aes(color = Year), size = 1) +
  theme_minimal()
```

### Analysing the NA values

```{r observing NA values, echo=FALSE}
#Observing data with NA values
animals_slaughtered_for_meat[rowSums(is.na(animals_slaughtered_for_meat)) > 0, ]
```

Observing the NA values with NA values in the code column

```{r observing data with NA values in the code column,echo=FALSE}
#Observing data with NA values in the code column
animals_slaughtered_for_meat[is.na(animals_slaughtered_for_meat$Code), ]
```

Cleaning the rows without code.
```{r Cleaning codes for continents,echo=FALSE}
#Because the code does not have codes for the continents, it is necessary to erase those rows.
#Delete columns without code (Only rows that are continents)
animals_slaughtered_for_meat <- animals_slaughtered_for_meat[!is.na(animals_slaughtered_for_meat$Code), ]
```


## Data of animals slaughtered after cleaning

Head of animals slaughtered after cleaning

```{r head of animals slaughtered after cleaning, echo=FALSE}
#head of data set
head(animals_slaughtered_for_meat)
```

Summary of animals slaughtered after cleaning

```{r summary of animals slaughtered after cleaning,echo=FALSE}
#Summary of data set
summary(animals_slaughtered_for_meat)
```


Observing the data with graphs after cleaning

```{r plot wiht by year and turkey after cleaning,echo=FALSE}
ggplot(animals_slaughtered_for_meat, aes(x = Year, y = Turkey)) + 
  geom_line(aes(color = Year), size = 1) +
  theme_minimal()
```


```{r subset of animals slaughtered, eval=FALSE, include=FALSE}
#Subset of Turkey and pigs due to missing data
#animals_slaughtered_for_meat <- subset(animals_slaughtered_for_meat, select = c(-Turkey, -Pigs))
```
